Web Service Community \\ Learning

### 2014-07-08 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Figure \ref{fig_community} represents the architecture of web service communities. The community is essentially a virtual group of web services having similar and complementary functionalities. Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as single web services. Web services join communities to increase their utility by having a larger market share and task pool. Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services for joining and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\begin{figure*}%[!t]
\centerline{\includegraphics[width=6.25in]{figures/community.eps}}
\caption{Architecture of web service communities}
\label{fig_community}
\end{figure*}

@@

	\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by wsj;o to a value v0 considered as
correct. The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.

@@

>>>>

The community of web services is essentially a virtual group of web services having similar and complementary functionalities. Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as single web services. Web services join communities to increase their utility by having a larger market share and task pool. Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services for joining and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

%\begin{figure*}%[!t]
%\centerline{\includegraphics[width=6.25in]{figures/community.eps}}
%\caption{Architecture of web service communities}
%\label{fig_community}
%\end{figure*}

@@

	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct. The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.

@@

In order to evaluate the real value of the quality metrics
